---
title: "Analysing Cookie Cats"
author: "Pau, Mikel, Pablo"
date: "2022-11-15"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```


## 1. Getting to know the datasets
```{r, echo=FALSE}
DS=read.csv("cookie_cats_ABtest.csv")
PR=read.csv("cookie_cats_purch.csv")
str(DS)
str(PR)
```

# 2. Preprocessing
## 2.1 Preprocessing dataset “Cookie Cats AB Testing”
First, we will change all the values in retention_1 to TRUE or FALSE. Then, we will remove all the NA values in the dataset. We located an user with almost 50.000 rounds played, so we also removed them.
```{r, echo=FALSE}
DS$retention_1[DS$retention_1=="false "]="FALSE"
DS$retention_1[DS$retention_1=="  true "]="TRUE"
DS=DS[-c(which(DS$sum_gamerounds>3000)), ]
DS=na.omit(DS)
table(DS$retention_1)
```

## 2.2  Preprocessing dataset “Cookie Cats Purchases”
First, we will change all the negative values in purch to positive, and remove the EUR chars. Then, we will remove all the NA values in the dataset.
```{r, echo=FALSE}
PR$purch=gsub("[-]", "", PR$purch)
PR$purch=gsub("[a-zA-Z]", "", PR$purch)
PR$purch=as.numeric(PR$purch)
PR=na.omit(PR)
table(PR$purch)
```

# 3. Descriptive analytics
## 3.1 Dataset “Cookie Cats AB Testing”
### 3.1.1 Users that downloaded the game
```{r, echo=FALSE}
TotalUsers=nrow(DS)
cat("Total number of users that downloaded the game: ", TotalUsers)
```
### 3.1.2 Distribution of users in groups
```{r, echo=FALSE}
DistributionUsers_labels=paste0(names(table(DS$version)), " = ", round(100*table(DS$version)/sum(table(DS$version)), 2), "% (", table(DS$version), ")")
pie(table(DS$version), labels=DistributionUsers_labels, main="Distribution of users in groups")
```

### 3.1.3 Game rounds
```{r, echo=FALSE}
boxplot(DS$sum_gamerounds[DS$version=="gate_30"], DS$sum_gamerounds[DS$version=="gate_40"], xlab="Groups", ylab="Num of Rounds", names=c("Gate_30", "Gate_40"), main="Game Rounds per each group")
Gate30gamerounds_mean=mean(DS$sum_gamerounds[DS$version=="gate_30"])
Gate30gamerounds_sd=sd(DS$sum_gamerounds[DS$version=="gate_30"])
Gate40gamerounds_mean=mean(DS$sum_gamerounds[DS$version=="gate_40"])
Gate40gamerounds_sd=sd(DS$sum_gamerounds[DS$version=="gate_40"])
cat("Gate 30 Mean: ", Gate30gamerounds_mean, " and Standard Deviation: ", Gate30gamerounds_sd)
cat("\nGate 40 Mean: ", Gate40gamerounds_mean, " and Standard Deviation: ", Gate40gamerounds_sd)
```
### 3.1.4 Retention (day 1 and day 7)
We can see that there is a retention rate of 44,52% for day 1, whereas for day 7 the rate is 18,61% 
```{r, echo=FALSE}
RetentionDay1_labels=paste0(names(table(DS$retention_1)), " = ", round(100*table(DS$retention_1)/sum(table(DS$retention_1)), 2), "%")
pie(table(DS$retention_1), labels=RetentionDay1_labels, main="Day 1 User Retention Rate")
RetentionDay7_labels=paste0(names(table(DS$retention_7)), " = ", round(100*table(DS$retention_7)/sum(table(DS$retention_7)), 2), "%")
pie(table(DS$retention_7), labels=RetentionDay7_labels, main="Day 7 User Retention Rate")
```

### 3.1.5 Are there non-playing users?
```{r, echo=FALSE}
NonPlayingUsers_pie=c(length(DS$sum_gamerounds[DS$sum_gamerounds==0]), length(DS$sum_gamerounds[DS$sum_gamerounds>0]))
NonPlayingUsers_labels=paste0(c("Non-playing users", "Playing users"), " = ", round(100*NonPlayingUsers_pie/sum(table(DS$sum_gamerounds)), 2), "%\n (", NonPlayingUsers_pie, ")")
pie(NonPlayingUsers_pie, labels=NonPlayingUsers_labels, main="Non-playing Users")
```

## 3.2 Dataset “Cookie Cats Purchases”
```{r, echo=FALSE}
barplot_labels=paste0(names(table(PR$purch)), "EUR")
barplot(table(PR$purch), xlab="Money Spent", ylab="Num of Users", names.arg=barplot_labels, main="Purchases made by users")
Purchases_mean=mean(PR$purch)
Purchases_sd=sd(PR$purch)
cat("Purchases Mean: ", Purchases_mean, " and Standard Devation: ", Purchases_sd)
```

# 4. Monetization metrics
```{r, echo=FALSE}
PayingUsers=length(PR$id)
ConversionRate=PayingUsers/TotalUsers
TotalRevenue=sum(PR$purch)
ARPU=TotalRevenue/TotalUsers
ARRPU=TotalRevenue/PayingUsers
hola=data.frame("Metrics" = c('Conversion Rate','ARPU','ARRPU'), "Values" = c(ConversionRate,ARPU,ARRPU))
knitr::kable(hola[1:2], caption = "Monetization Metrics", align = "cc")
```
# 5. A/B testing

## 5.1 Hypotheses

null: mean engagement gate 40 > mean engagement gate 30

Alternative: mean engagement gate 40 <= mean engagement gate 30

## 5.2 Visualisation
```{r, echo=FALSE}
boxplot(DS$sum_gamerounds[DS$version=="gate_30"], DS$sum_gamerounds[DS$version=="gate_40"], xlab="Groups", ylab="Num of Rounds", names=c("Gate_30", "Gate_40"), main="Game Rounds per each group")

Gate30gamerounds_mean=mean(DS$sum_gamerounds[DS$version=="gate_30"])

Gate30gamerounds_sd=sd(DS$sum_gamerounds[DS$version=="gate_30"])

Gate40gamerounds_mean=mean(DS$sum_gamerounds[DS$version=="gate_40"])

Gate40gamerounds_sd=sd(DS$sum_gamerounds[DS$version=="gate_40"])

cat("Gate 30 Mean: ", Gate30gamerounds_mean, " and Standard Deviation: ", Gate30gamerounds_sd)

cat("\nGate 40 Mean: ", Gate40gamerounds_mean, " and Standard Deviation: ", Gate40gamerounds_sd)

pie(c(sum(DS$sum_gamerounds[DS$version=="gate_30"]), sum(DS$sum_gamerounds[DS$version=="gate_40"])), labels = paste0(c("Gate 30", "Gate 40"), " = ", c(sum(DS$sum_gamerounds[DS$version=="gate_30"]), sum(DS$sum_gamerounds[DS$version=="gate_40"]))), main = "Total game rounds per group")
```

##5.3 Computation



# 6. Regression analysis
```{r, echo=FALSE}
##USAR LIBRERIA MERGE

```

# 7. Dashboard

# 8. Conclusion

# 9. Team contribution


# 10. Non-cheating manifesto



